Solutions to Integer Programming from Quantum Annealing

### 2020-09-12 paper/main.tex
added sentence about g.s asymmetry

We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis. \cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}
Converting to the Ising representation of the the problem Hamiltonian,
\begin{equation}
    \label{eq:HIsing}
     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
\end{equation}
we can recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties. More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~{\color{red} cite some AL papers here} \cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
dd

Our improvement strategy is motivated by the MBL hypothesis.
That is, we want the system to be ergodic and avoid the MBL phase.
As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.\cite{doi:10.7566/JPSJ.89.044001}

@@

The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
All other states receive negligible probability at the end of annealing.
The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.

>>>>

We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis. \cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}
Converting to the Ising representation of the the problem Hamiltonian,
\begin{equation}
    \label{eq:HIsing}
     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
\end{equation}
we can recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties. More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
dd

Our improvement strategy is motivated by the MBL hypothesis.
That is, we want the system to be ergodic and avoid the MBL phase.
As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields~\cite{doi:10.7566/JPSJ.89.044001}.

@@

The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
All other states receive negligible probability at the end of annealing.
The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
The asymmetry in the ground state distribution is a result of annealing offsets lifting the ground state degeneracy. Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.
